\mytitle

### 2012-05-23 papers/SAS2012/implicitization.tex
remarques de Sriram, #1

\section{Disjunctive Invariants}
\label{sec:disjunctive}

@@

>>>>

\section{Disjunctive Invariants}
\label{sec:disjunctive}
While many (most?) useful program invariants on numerical variables can be expressed as conjunctions of inequalities and congruences, it is sometimes necessary to introduce disjunctions.
For instance, the loop \lstinline|for (int i=0; i<n; i++) {...}| has head invariant $0 \leq i \leq n \lor (i=0 \land n<0)$.
For this very simple example, a simple syntactic transformation of the control structure (into \lstinline|i=0; if (i<n) do {...} while (i<n)|) is sufficient, but in more complex cases more advanced analyses are necessary
\cite{DBLP:conf/emsoft/BalakrishnanSIG09,DBLP:journals/fmsd/Jeannet03,DBLP:conf/cav/SharmaDDA11,Monniaux_Bodin_APLAS11};
in intuitive terms, they discover \emph{phases} or \emph{modes} in loops.

@@

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "implicitization_lmcs.tex"
%%% reftex-cite-format: natbib
%%% End:
